Rate of Information 

### 2019-01-23 cogsci/position-info.Rmd
working on rewriting intro

When people communicate in speaking or writing, they can have a variety of different goals. Perhaps the most important of these goals is to communicate information. If we take this as the primary goal of communication, then how information is transmitted should have regular properties. There is a rich literature on information, dating back to Claude Shannon’s theory of information (1948). We know from Shannon’s work that rate of information transmission should be constant and as close as possible to the capacity of the communication channel. Levy & Jaeger (2007) introduce the *uniform information density* hypothesis, arguing that speakers structure utterances so as to optimize information density. Viewing human communication as a noisy channel, the authors argue that speakers and writers should attempt to communicate information as evenly as possible and as close to the channel capacity as possible. Their evidence comes in the form of the use or lack thereof of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus (CITATION).

Zhan and Levy (2018) study Mandarin Chinese classifier use, and find that the use of specific classifiers, versus general classifiers, appears more often in cases where the production of the corresponding noun is more difficult than when the production is easier, as would be predicted by the UID perspective.

In Yu et al. (2016), the authors challenge the UID perspective through computing the unigram positional entropy within the text portion of the British National Corpus (BNC). We follow Yu et al. (2016) in using the following formula for each word position X of sentences of fixed length k from the corpus, where each $w$ is a word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position X divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. [Give the equation its own paragraph]

>>>>

When people communicate in speaking or writing, they can have a variety of different goals. Perhaps the most important of these goals is to communicate information. If we take this as the primary goal of communication, then how information is transmitted should have regular properties. From Shannon (1948), we know that when information is being communicated, the rate of information transmission should be constant and as close as possible to the capacity of the communication channel to optimally transmit the information. Levy & Jaeger (2007) introduce the *uniform information density* (UID) hypothesis, arguing that speakers structure utterances so as to optimize information density. Viewing human communication as a noisy channel, the authors argue that speakers and writers should attempt to communicate information as evenly as possible and as close to the channel capacity as possible. Their evidence concerns the use or lack of use of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus.

However, some recent work has contradicted the UID hypothesis. Zhan and Levy (2018) study Mandarin Chinese classifier use for specific and general Mandarin classifiers. Specific classifiers are specific to certain nouns, and UID would predict that specific classifiers would appear when the production of the corresponding noun is easier, to spread the information contained by the classifier and noun less densely over time. General classifiers can be applied to any noun and contain no special information content. Zhan and Levy find that speakers use specific classifiers  more often in cases where the production of the corresponding noun is more difficult than when the production is easier; speakers do not avoid unexpected peaks in information content for their listeners, but instead maximize their ease of production.

In Yu et al. (2016), the authors challenge the UID perspective through computing the unigram positional entropy within the text portion of the British National Corpus (BNC). We follow Yu et al. (2016) in using the following formula for each word position X of sentences of fixed length k from the corpus, where each $w$ is a word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position X divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$.
